A matter of operationalization: Paradigm and stimulus [feature] selection impacts localization of "parahippocampal place area"

### 2020-12-16 paper/main.tex
rewrite abstract; plan for structure

% title has to be < 110 chars incl. spaces
%  at the moment 109 Chars
\title{Hemodynamic responses of the anterior "parahippocampal place area" (PPA) to a Hollywood movie's audio-description}

@@

\begin{abstract}
% < 170 words new analysis of existing data of interest to a broad section of
% our audience highlighting innovative examples of data reuse may be used to
% present compelling new findings & conclusions derived from published.  intro
Neuroimaging studies have parcellated the human brain into distinct functional
areas.
% PPA
A region in the human hippocampal cortex termed ``parahippocampal place area''
is classically considered to be a higher visual area as increased hemodynamic
activity in the PPA correlates with the perception of static pictures of
landscapes compared to pictures of faces or objects.
% What we do
In the current study, we exploratorily tested if spatial information embedded in
a Hollywood movie and its audio-description of (i.e. the movie's soundtrack with
an additional narrator) correlates with increased hemodynamic activity in the
PPA.
%
We use publicly available functional magnetic resonance imaging data
(studyforrest.org) of 14 subjects to build canonical general linear model (GLM)
$t$-contrasts and compare current results to results that we gained from a
dedicated visual localizer experiment conducted with same participants.
% compare to visual localizer experiment group results
On a group average level, results of our whole brain analyses show significantly
increased activation restricted to the anterior part of the PPA that was defined
using the visual localizer [as well as in the retrosplenial and lateral
occipital cortex] of both hemispheres.
% individual results
On an individual level, results show significant bilateral clusters in the
anterior PPA of nine subjects and significant unilateral clusters in two
subjects.
% conclusion: generalizability
Results suggest that increased activation in the PPA during the perception of
static pictures generalizes to the perception of auditorily presented spatial
information.
% conclusion: PPA has subregions
Lastly, our results provides further evidence that the PPA can be divided into
functional subregions.\end{abstract}

@@

>>>>

% title has to be < 110 chars incl. spaces at the moment 109 Chars
\title{A matter of operationalization: Paradigm and stimulus [feature] selection
impacts localization of "parahippocampal place area"}

@@

\begin{abstract}
% < 170 words new analysis of existing data of interest to a broad section of
% our audience highlighting innovative examples of data reuse may be used to
% present compelling new findings & conclusions derived from published.  intro
Neuroimaging studies have parcellated the human brain into distinct functional
areas.
% PPA
A region in the human hippocampal cortex termed ``parahippocampal place area''
is classically considered to be a higher visual area as increased hemodynamic
activity in the PPA correlates with the perception of static pictures of
landscapes compared to pictures of faces or objects.
% AV, AD: operationalization
In this study, we explore different ways to operationalize spatial perception in
14 subjects that were watching an audio-visual Hollywood movie and listened to
the audio-description of the same movie (studyforrest.org).
% auditory localizer?
Focussing on the audio-description, we further test if an auditory narrative
could substitute localize a ``visual area'' in individual subjects.
% GLM
For each naturalistic stimulus, we model hemodynamic activity via several
general linear model (GLM) $t$-contrasts that are based on stimulus annotations
/ selected stimulus features.
% VIS
Current results are compared to results of classic visual localizer experiment
that we conducted previously to localize the PPA in the same participants
\citep{sengupata2016extension}.
% results: group AV
On a group level, results of our current approach to operationalize the
perception of space during a movie reveal significantly increased hemodynamic
activity spatially overlapping with the PPA but also extending into early visual
cortices.
% results: group AD
Results of the audio-description reveal significant activation restricted to the
anterior part of the PPA.
% results: individual AD
On an individual level, results of the audio-description show significant
bilateral clusters in the anterior PPA of nine subjects and significant
unilateral clusters in two subjects.
% conclusion: generalizability
Results suggest that increased activation in the PPA during the perception of
static pictures generalizes to the perception of spatial information embedded in
an audio-visual movie and an exclusively auditory stimulus.
% conclusion: PPA has subregions
Our results provides further evidence that the PPA can be divided into
functional subregions.
% localizer substitute
An auditory narrative might substitute a visual paradigm to localize the PPAs
anterior part in visually impaired subjects.\todo{very bold claim to be written
in the abstract}

\end{abstract}
\todo[inline]{RSC \& LOC are not mentioned in the abstract (anymore)}

@@

\section*{Keywords}
% maximal 8
fMRI, naturalistic stimulus, spatial perception, vision, language, speech,
narrative, studyforrest

\pagebreak[4]

\section*{Plan}

\noindent Abstract:

\begin{itemize}
\item missing: the exact (!) presumed PPA function? spatial perception, scene
    representation, spatial layout hypothesis, associative processing? the list
    is endless when it comes what the PPA processes exactly (in pictures)
\item operationalization in two naturalistic stimuli (ecological validity not
    mentioned anymore)
\item AV: ?
\item AD: also as functional localizers
\item Results: ``spatial perception'' can differently operationalized via
    naturalistic stimuli -> we get similar results; AD is restricted to
    anterior PPA; narrative as ``visual localizer''(??)
\end{itemize}

\noindent Intro:

\begin{itemize}
\item presumed function of the PPA? -> spatial layout hypothesis and,
    unfortunately, others
\item question: is localization of proposed PPA function using visual localizer
    valid?
\item why do we use three datasets? To answer question (of presumed function of
    PPA?) that is usually operationalized using pictures (but: big controversy
what exactly in pictures the PPA processes; Aminoff tries to unify the
    arguments)
\item VIS: connection to literature; problem: stimulus validity re PPA function
\item AV: more ecologically valid; problem: of operationalization; why did we do
    it the done way (-> probably issue of method section)
\item AD: alternative stimulus for proposed function but verbal/semantic
    information
\end{itemize}

\noindent Method (after stimulus description):

\begin{itemize}
\item key strategy to address this question
\item which specific cognitive processing do we contrast in AD vs. AV?
\item ``ingredients'' to make it happen? we have some annotations at hand;
    define congruent contrasts based on regressors that are built from
    annotations; available annotations could be described in a dedicated
    section (COH: should be shorty and very high-level; details probably will
    confuse the shit out of readers)
\item what do we need to check to ensure subsequent analyses are valid (COH:
    this is the part that is the most elusive to me when it comes to precise
    phrasing)? a) correlation of regressors, b) negative controls
\end{itemize}

\pagebreak[4]
